---
title: "EDLD 652 Homework"
author: "Ksenia Gordeeva, Rebeccca Gordon, Amy Warnock"
date: "2/28/2022"
output:
  html_document:
   code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
											warning = FALSE)

library(tidyverse)
library(rio)
library(here)
#install.packages("ggtext")
library(ggtext)
#install.packages("extrafont")
library(extrafont)
library(colorspace)
library(janitor)
library(ggtext)
library(ggrepel)
library(gghighlight)
library(ggforce)
```

## Question 1
Use the transit costs data to reproduce the following plot. To do so, you will need to do a small amount of data cleaning, then calculate the means and standard errors (of the mean) for each country. Please filter to only counties with at least three observations. To use actual country names, rather than abbreviations, join your dataset with the output from the following
```{r transit-costs-se, results = 'hide'}
transit_cost <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-01-05/transit_cost.csv')
#install.packages("tidytuesdayR")
#transit_cost <- tidytuesdayR::tt_load(2021, week = 2)


#install.packages("countrycode")
country_codes <- countrycode::codelist %>% 
	select(country_name = country.name.en, country = ecb)

country2 <- right_join(country_codes, transit_cost)

country2 %>% 
  group_by(country_name) %>% 
  count(country_name)

transit2 <- country2 %>% 
	group_by(country_name) %>% 
	summarize(
		mean_cost = mean(as.numeric(real_cost), na.rm = TRUE),
		se_cost = sd(real_cost, na.rm = TRUE)/ sqrt(n()),
		lower = as.numeric(mean_cost) + qnorm(0.025) * se_cost,
		upper = as.numeric(mean_cost) + qnorm(0.975) * se_cost,
		N = n()
	) %>% 
	mutate(country_name = fct_reorder(country_name, mean_cost)) %>% 
	na.omit() %>% 
	filter(N > 2)
```

```{r transit-costs-se-plot, fig.width = 6, fig.height = 8}
ggplot(transit2, aes(mean_cost, country_name)) +
	geom_linerange(aes(xmin = lower, xmax = upper), 
	               color = "gray30", size = .5) +
	geom_point(color = "#6495ed") +
	scale_x_continuous(labels = scales::comma,
									   expand = c(0, 0)) +
  coord_cartesian(xlim = c(0, 35000)) +
	labs(
		title = "Cost to build transit systems vary by country",
		caption = "Data provided through #tidytuesday by the Transit Costs Project",
		x = "Real Cost (In millions of dollars)",
		y = "Country"
	) + 
	theme_minimal() + 
	theme(plot.subtitle = element_markdown(),
	      panel.grid.major.y = element_blank(),
	      panel.grid.minor.x = element_blank()
	      ) +
  theme(plot.title.position = "plot")  
```

## Question 2
Visualize the same relation, but displaying the uncertainty using an alternative method of your choosing.
```{r tranist-costs-CI, fig.width = 7.8, fig.height = 8}
ggplot(transit2, aes(country_name, mean_cost)) +
	geom_hline(yintercept = 0,
						 color = "white",
						 linetype = 2) +
	geom_errorbar(aes(ymin = mean_cost + qnorm(.025)*se_cost, 
										ymax = mean_cost + qnorm(.975)*se_cost,
										color = "95%"),
								width = 0.2,
								size = 0.8) + 
	geom_errorbar(aes(ymin = mean_cost + qnorm(.05)*se_cost, 
										ymax = mean_cost + qnorm(.95)*se_cost,
										color = "90%"),
								width = 0.2,
								size = 1.2) + 
	geom_errorbar(aes(ymin = mean_cost + qnorm(.1)*se_cost, 
										ymax = mean_cost + qnorm(.9)*se_cost,
										color = "80%"),
								width = 0.2,
								size = 1.6) + 
	scale_color_manual("Confidence Interval",
										 values = c("#3BC5FB",
										 					 "#F78A2F",
										 					 "#F31E1E")) +
	scale_y_continuous(labels = scales::comma,
	                   limits = c(0, 35000),
										 expand = c(0, 0)) +
	geom_point(alpha = .5) +
	coord_flip() +
	labs(
		title = "Cost to build transit systems vary by country",
		caption = "Data provided through #tidytuesday by the Transit Costs Project",
		y = "Real Cost (In millions of dollars)",
		x = "Country"
	) + 
	theme_minimal() + 
	theme(plot.subtitle = element_markdown(),
	      panel.grid.major.y = element_blank(),
	      panel.grid.minor.x = element_blank()
	      ) +
  theme(plot.title.position = "plot") 
```

## Question 3
Compute the mean length and real_cost by city. Reproduce the following plot.
```{r q3-data}
transit <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-01-05/transit_cost.csv')

country2 <- right_join(country_codes, transit)

transit <- country2 %>% 
  select(country,
         country_name,
         city, 
         real_cost,
         length) 

transit2 <- transit %>% 
	group_by(city, country, country_name) %>% 
	summarize(
		mean_cost = mean(as.numeric(real_cost), na.rm = TRUE),
		mean_length = mean(length, na.rm = TRUE), 
		line_number = n())  %>% 
	na.omit() 
```
```{r q3-plot}
ggplot(data = transit2, aes(x = mean_length, y = mean_cost)) +
    geom_point(aes(size = line_number), color =  "#9932CC", alpha = 0.9) +
    scale_y_log10(labels = scales::dollar) +
    scale_x_log10() +
  scale_size_binned(breaks=c(1,5,10,20,25),
                    labels=c("1","5","10","20","25"),
                    limits = c(1,25)) +
    labs(size="Number of transit systems",
         title = "Longer transit systems tend to cost more",
         subtitle = "<span style = 'color: #9932CC;'>India</span> has among the most transit systems in the world",
         x = 'Average length',
         y = 'Average cost',
        caption = "Note the axis are on  the log scale") +
    gghighlight(country == "IN") +
  geom_text_repel(data = filter (transit2,
                                 country == "IN"),
                  aes(label = city),
                  min.segment.length = 0,
                  box.padding = 0.75)+
 guides(size = guide_bins(direction = "horizontal"))+
  theme_minimal(base_size = 15) +
  theme(plot.title.position = "plot", 
        legend.position = "bottom",
        plot.subtitle = element_markdown())
```

## Question 4
Using basically the same data, reproduce the following plot. Note you’ll need the country_name column in your dataset.
```{r q4}
ggplot(data = transit2, aes(x = mean_length, y = mean_cost)) +
  geom_point(aes(size = line_number), color =  "gray80", alpha = 0.9) +
  geom_point(data = filter(transit2, country == "US"),
             color = "#1E90FF") +
  scale_y_log10(labels = scales::dollar) +
  scale_x_log10() +
  geom_mark_ellipse(aes(group = country_name, label = country_name),
                    data = filter(transit2,
                                  country_name == "United States"),
                    label.colour = "#1E90FF",
                    con.colour = "#C55644",
                    color = "#C55644") +
  scale_size_binned(breaks=c(1,5,10,20,25),
                    labels=c("1","5","10","20","25"),
                    limits = c(1,25)) +
    labs(size="Number of transit systems",
         title = "Longer transit systems tend to cost more",
        x = 'Average length',
        y = 'Average cost',
        caption = "Note the axis are on  the log scale") +
  geom_label_repel(data = filter (transit2,
                                 country == "US"),
                   aes(label = city),
                   min.segment.length = -0.5,
                   box.padding = 0.75,
                   color = "gray70") +
  guides(size = guide_bins(direction = "horizontal")) +
  theme_minimal(base_size = 10) +
  theme(plot.title.position = "plot", 
        legend.position = "bottom",
        plot.title = element_text(size = 20),
        axis.title = element_text(size = 14),
        legend.title = element_text(size = 14))
```
## Question 5

Replicate this plot, but compare the Barnum neighborhood to the Barnum-West neighborhood. (Note: I decided to start with replicating the original quantile dotplot to make sure I was on the right track.)
```{r q5-data}
#FYI: I added the crime.csv file to the .gitignore file, so it will not be in the "data" folder pulled from github

crime <- import(here("data", "crime.csv")) %>%
  as_tibble() %>% 
  clean_names()
```

```{r q5-model}
model_data <- crime %>% 
  mutate(neighborhood_id = relevel(factor(neighborhood_id), ref = "barnum"))

m <- glm(is_crime ~ neighborhood_id, 
         data = model_data,
         family = "binomial")

tidied <- broom::tidy(m)
```

```{r regis-prep}
regis <- tidied %>% 
  filter(term == "neighborhood_idregis")

discretized <- data.frame(x = qnorm(ppoints(20), 
                                    mean = regis$estimate,
                                    sd = regis$std.error)) %>%
  mutate(crimeprob = ifelse(x > 0, "#21B48E", "#8A7D98"))
```

```{r regis-plot, fig.width = 6, fig.height = 7}
discretized %>% 
  ggplot(aes(x)) +
  geom_dotplot(aes(fill = crimeprob), binwidth = .0425) +
  scale_fill_identity(guide = "none") +
  geom_vline(xintercept = 0,
             color = "#D04244",
             size = 1) +
  theme_minimal() +
  scale_y_continuous(expand = c(0,0), name = "", breaks = NULL) + 
  coord_cartesian(ylim = c(0, .8)) +
  scale_x_continuous(breaks = c(-0.10, -.05, 0, .05, .10)) +
  labs(x = "Difference in log odds of a crime being committed",
       caption = "Each ball represents 5% probability",
       title = "</span>Probability of differential crime rates between neighborhoods<br></span><span style = 'color:#8A7D98;'>**Regis**</span>
compared to <span style = 'color:#21B48E;'>**Barnum**</span>"
  ) +
  theme(
    text = element_text(),
    plot.title.position = "plot",
    plot.title = element_markdown(lineheight = 1.2)
  )
```

```{r barnumwest-prep}
barnumwest <- tidied %>% 
  filter(term == "neighborhood_idbarnum-west")

discretized_bnw <- data.frame(x = qnorm(ppoints(20), 
                                        mean = barnumwest$estimate,
                                        sd = barnumwest$std.error)) %>%
  mutate(crimeprob = ifelse(x > 0, "#21B48E", "#8A7D98"))
```


```{r barnumwest-plot, fig.width = 6, fig.height = 6.5}
discretized_bnw %>% 
  ggplot(aes(x)) +
  geom_dotplot(aes(fill = crimeprob), binwidth = .037) +
  scale_fill_identity(guide = "none") +
  geom_vline(xintercept = 0,
             color = "#D04244",
             size = 1.5) +
  theme_minimal() +
  scale_y_continuous(expand = c(0,0), name = "", breaks = NULL) + 
  coord_cartesian(ylim = c(0, .75)) +
  scale_x_continuous(breaks = c(-0.10, -.05, 0, .05, .10)) +
  labs(x = "Difference in log odds of a crime being committed",
       caption = "Each ball represents 5% probability",
       title = "</span>Probability of differential crime rates between neighborhoods<br><span style = 'color:#8A7D98 ;'>**West-Barnum**</span>
compared to <span style = 'color:#21B48E;'>**Barnum**</span>"
  ) + 
  theme(
    text = element_text(),
    plot.title.position = "plot",
    plot.title = element_markdown(lineheight = 1.2)
  )
```

